Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-17 documents/BrazilSlides/slides.tex
new noise figures, new code to plot distributions, references, other stuff to come in the morning

\documentclass[
    hyperref={bookmarks=false},% ,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue
    xcolor={dvipsnames},
]{beamer}

@@

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\setbeameroption{show notes} % Shows notes on the right of the main slides
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[backend=biber, citestyle=authoryear]{biblatex} %

@@

\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
\setbeamertemplate{bibliography item}{\insertbiblabel}
\addbibresource{../references.bib}

@@

\frame{\titlepage}

% \begin{frame}
%     \frametitle{Table of Contents}
% \tableofcontents

% \end{frame}

\begin{frame}
    \frametitle{Introduction}
    \note[item]{Thank International Institute for Physics (IIP) for support}
    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
\end{frame}
\begin{frame}
    \frametitle{Objective}
    \begin{itemize}
        \item Derive causal compatibility/locality inequalities that distinguish quantum distributions from classical ones
        \item Specifically for the Triangle Scenario (TS)
    \end{itemize}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
    \note[item]{More specifically, the ambition of the project is to obtain such inequalities that constraint compatibility with The Triangle Scenario}
    \note[item]{Triangle Scenario has be studied extensively before}
    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility}
    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
\end{frame}

\begin{frame}
    \frametitle{Objective Cont'd}
    \note[item]{At the time of publishing~\cite{Branciard_2012}, problem seems hard.}
    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{itemize}
        \item Report the discovery of such inequalities
        \item Explain how these inequalities were obtained
        \item Discuss quantum distributions that violate compatibility inequalities
        \item Attempts at finding new quantum distributions different than those proposed by~\cite{Fritz_2012}
        \item Briefly discuss symmetric inequalities
    \end{itemize}
    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
    \note[item]{Additionally I will talk about my attempts at using these inequalities to find new incompatible quantum distributions}
    \note[item]{In doing so, will discuss how we obtained symmetric compatibility inequalities that have violations in the Triangle Scenario}
\end{frame}

@@

\begin{frame}
    \frametitle{Fritz Distribution}
    The \term{Fritz Distribution $\prob[F]$}:
    \begin{itemize}
        \item three-party $\prob[F] = \prob[ABC]$
        \item each party has $4$ outcomes
    \end{itemize}
    \begin{gather*}
    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
    \end{itemize}
    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Results}
    \begin{itemize}
        \item Full rank $\rho, M$ gives $81$ free parameters
        \[ \abs{\la} = 3 \cdot (12 + 3) + 3 \cdot 12 = 81 \]
        \item Parameterization of quantum distributions still degenerate
        \item Noisy seed (Gaussian noise):
        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
        \item Uniform seed:
        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
    \end{itemize}

>>>>

\documentclass[
    hyperref={bookmarks=false},% ,, linkcolor=blue, urlcolor=blue,, colorlinks=true, citecolor=MidnightBlue
    xcolor={dvipsnames},
]{beamer}

@@

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\AtBeginNote{\scriptsize} % Make notes small
\setbeameroption{show notes} % Shows notes
% \setbeameroption{show only notes} % Shows only notes
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %

\setbeamertemplate{navigation symbols}{
\insertslidenavigationsymbol%
\insertframenavigationsymbol%
\insertsubsectionnavigationsymbol%
\insertsectionnavigationsymbol%
\insertdocnavigationsymbol%
\insertbackfindforwardnavigationsymbol%
\hspace{1em}%
\usebeamerfont{footline} \insertframenumber/\inserttotalframenumber%
}

@@

\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
\setbeamertemplate{bibliography item}{\insertbiblabel}
\addbibresource{../references.bib}
\AtBeginBibliography{\small}

@@

\begin{frame}
    \titlepage
    \note[item]{Thank International Institute for Physics (IIP) for support}
    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
\end{frame}

\begin{frame}
    \frametitle{The Triangle Scenario (TS)}
    \begin{center}
        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
    \note[item]{Triangle Scenario has be studied extensively before}
    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Report the discovery of such inequalities
        \item Explain how these inequalities were obtained
        \item Symmetric inequalities
        \item Greater violations
        \item Different kinds of non-locality?
    \end{enumerate}
    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
    \note[item]{Talk about how symmetries play two roles in the search for quantum non-locality}
    \note[item]{Demonstrate how these inequalities are robust to noise}
    \note[item]{Finding maximally violating distributions}
\end{frame}

@@

\newcommand{\probplotvalue}[1]{%
    \definecolor{probvalcolor}{RGB}{#1}%
    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
        \pgfmathsetmacro{\size}{0.2};%
        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
    \end{tikzpicture}%
}%

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Course Graining CHSH [Optional]}
    \begin{gather*}
    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
    \end{itemize}
    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Results}
    \begin{itemize}
        \item Full rank $\rho, M$ gives $81$ free parameters
        \[ \abs{\la} = 3 \cdot (12 + 3) + 3 \cdot 12 = 81 \]
        \item Parameterization of quantum distributions still degenerate
        \item Noisy seed (Gaussian noise):
        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
        \item Uniform seed:
        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Uniform Noise}
    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    % \begin{center}
    %     \begin{tikzpicture}
    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
    %         \draw[] (1*\ts,0) node[]{$=$};
    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
    %         \draw[] (3*\ts,0) node[]{$+$};
    %         \draw[] (4*\ts,0) node[]{$\delta$};
    %     \end{tikzpicture}
    % \end{center}
\end{frame}
